\documentclass[letterpaper,10pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{20pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!50!red,
    linkbordercolor=red,
    urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
    \item\small{
        \ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
    }
}

\usepackage[dvipsnames]{xcolor}
\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & \textcolor{mygray}{#2}                 \\
        \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & \textcolor{mygray}{#2}                 \\
        \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
        {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}      & \textcolor{mygray}{#2}                 \\
        \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}


\begin{document}

\vfill\noindent
\begin{tabular}[t]{@{
\vspace{0.5ex}
}left}
\textbf{\large{Artyom Fadeyev}} \\
\address{
+7\hspace{0.5ex}921\hspace{0.5ex}060\hspace{0.5ex}05\hspace{0.5ex}05 $\cdot$ Saint-Petersburg, Russia
}
\end{tabular}
\hfill % move it to the right
\begin{tabular}[t]{@{
\vspace{0.5ex}
}center}
\href{mailto:fadyat@icloud.com}{\color{black} fadyat@icloud.com} \\

\href{https://github.com/fadyat}{\color{black} \faGithub}

\href{https://www.linkedin.com/in/fadyat/}{\color{black} \faLinkedin}

\href{https://t.me/not_fadyat}{\color{black} \faTelegram}
\end{tabular}


\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National Research University ITMO}
{Saint-Petersburg, Russia}
{Software Engineering}
{Sept. 2020 - Aug. 2024 (Present)}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeExpSubheading
{\href{https://www.tinkoff.ru/career}{Tinkoff}}{Saint-Petersburg, Russia}
{SRE Intern, DWH Ingest}{March 2023 - June 2023}
{\skill{K8S} \skill{Gitlab CI} \skill{Grafana} \skill{Prometheus} \skill{Kafka}}
\resumeDesc{
\begin{itemize}
\item Set up a project CI/CD pipeline using Gitlab CI and deploy it to a Kubernetes cluster using Helm.
\item Implemented Prometheus and Grafana-based alert systems to notify duty engineers about service issues promptly.
\item Changed usage of the GitLab artifacts to the Artifactory registry with fully automated building, publishing, and deployment.
\item Jointly implemented transferring a Kafka topic from one cluster to another using the Java and Schema Registry.
\end{itemize}}


\resumeExpSubheading
{\href{https://www.playrix.com/en/}{Playrix}}{Vologda, Russia}
{SWE Intern, Automation Team}{July 2022 - Sept. 2022}
{\skill{Python} \skill{SQL} \skill{AWS}}
\resumeDesc{
\begin{itemize}
\item Developed a solution for tracking employee birthdays and length of service, with delayed notifications in Slack and Asana.
\item Learned to write asynchronous code and understood AWS queues, for example, Kinesis.
\item Deployed services using Docker and Nomad orchestrator with storing secrets in Vault and configurations in Consul.
\end{itemize}}

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

\resumeProjSubheading
{\href{https://github.com/fadyat/i4u}{i4u}}{}
{\skill{Go} \skill{OpenAI} \skill{Gmail}}{Aug. 2023 - Present}
\resumeDesc{
\begin{itemize}
\item Internship for you is a lightweight and efficient solution designed to streamline the management of internship requests.
\item Automates reading, identifying, summarizing, and forwarding internship-related emails.
\item Design employs the principles of concurrency by utilizing goroutines, channels, and wait groups.
\end{itemize}
}

\resumeProjSubheading
{\href{https://github.com/fadyat/segments}{segments}}{}
{\skill{Go} \skill{PostgreSQL} \skill{Swagger} \skill{Docker}}{Aug. 2023 - Sept. 2023}
\resumeDesc{
\begin{itemize}
\item Developed a backend service for dynamic user segmentation, enabling flexible experimentation and targeted user grouping.
\item Implemented real-time history tracking, allowing precise monitoring of user segment membership changes.
\item Introduced time-based membership management, allowing control over user segment membership durations.
\item Engineered an automated user distribution feature, simplifying segmentation and testing through predefined percentages.
\end{itemize}
}

\resumeProjSubheading
{\href{https://github.com/fadyat/hooks}{hooks}}{}
{\skill{Go} \skill{Docker} \skill{Gitlab} \skill{Asana}}{Feb. 2023 - June 2023}
\resumeDesc{
\begin{itemize}
\item Hooks streamlines workflows by integrating GitLab with Asana, automating task tracking and commits.
\item Utilizes GitLab webhooks for real-time synchronization of tasks with the latest commits, ensuring project accuracy.
\item Asana tasks are pinned to GitLab merge request descriptions, providing comprehensive project monitoring.
%\item Achieves fully automated build and publishing to the Docker registry for a smooth development process.
\end{itemize}
}

%\resumeProjSubheading
%{\href{https://github.com/fadyat/cloud}{Cloud programming with Go}}{}
%{\skill{Go} \skill{MongoDB} \skill{Docker}}{Oct. 2022 - Dec. 2022}
%\resumeDesc{
%Covered the software architectural patterns of cloud applications and practical concepts regarding how to scale, distribute, and deploy those applications.
%}

%\resumeProjSubheading
%{\href{https://github.com/fadyat/asana-tools}{Asana tools}}{}
%{\skill{Python} \skill{React} \skill{OAuth2} \skill{Docker}}{September 2022}
%\resumeDesc{
%A service that will help you automate the work with tasks in Asana.
%Allows you to create a task based on the submitted template, and also allows you to create a report
%that allows you to set approvals and rejections for contractor tasks for
%a certain period of work.
%}


%\resumeProjSubheading
%{\href{https://github.com/ITMO-TECH-TEAM-3/TEAM-3-1}{Sports events}}{}
%{\skill{Java} \skill{Spring} \skill{Python} \skill{Freemarker}}{May 2022}
%\resumeDesc{Learned the Java and Spring framework. Implemented all the basic structure and internal code logic
%(endpoints, authorization, deployment) of a service that can serve users, collaborated with 3 teams of 3 students each.
%\\ Partly played the role of team leader. Constantly created new tasks and discussed them with the team.}

%\resumeProjSubheading
%{\href{https://github.com/fadyat/ITMO-PROBLEMS/tree/master/Programming-Technologies/IV\%20semester}{Code fixer and analyzer}}{}
%{\skill{C\#} \skill{Roslyn} \skill{LINQ}}{March 2022}
%\resumeDesc{
%The analyzer finds the if statement and displays a warning that you can invert it. Upon acceptance, the code fixer
%inverts the operator. There is also the detection of private fields that are used as local.
%It was developed using Roslyn analyzer and abstract syntax tree parsing.
%}

\resumeSubHeadingListEnd

\section{Achievements}
\resumeSubHeadingListStart

\resumeProjSubheading
{{\href{https://yandex.ru/yaintern/schools/summer}{Yandex School of Backend Development}}}{}
{\skill{Go} \skill{PostgreSQL} \skill{gRPC}}
{June - Aug 2023}
\resumeDesc{
\begin{itemize}
\item Collaborated in an 11-member team to develop a platform for student allocation between projects based on preferences.
\item Led the implementation of role-based access control, ensuring secure user interactions and data integrity.
\item Designed and executed the database architecture, optimizing data storage and retrieval processes.
\item Played a proactive role in the end-to-end project development, contributing significantly to API development and frontend design.
\end{itemize}
}

\resumeProjSubheading
{{\href{https://education.vk.company/students}{VK Advanced Python}}}{}
{\skill{Python} \skill{C}}
{March - May 2023}
\resumeDesc{
\begin{itemize}
\item Acquired expertise in advanced Python concepts, including asynchronous programming, C extensions, and metaclasses.
\item Developed a C extension enabling seamless integration with a C library for JSON manipulation.
\end{itemize}
}

%\resumeProjSubheading
%{{\href{https://github.com/Hacktoberfest}{GitHub Hacktoberfest}}}{}
%{\skill{Opensource} \skill{Git}}
%{Oct. 2021}
%\resumeDesc{Contributed to an open source in time of the Hacktoberfest event and take a prize.
%}

%\resumeProjSubheading
%{{Phystech olympiad of mathematics}}{}
%{\skill{Mathematics}}
%{Febr. 2020}
%\resumeDesc{Prize-Winner of the All-Russian Olympiad, organized by the MIPT, which allows you to enter a university without exams
%}

%\resumeProjSubheading
%{{Russian National Olympiad in Informatics}}{}
%{\skill{C++} \skill{Competitive programming}}
%{Jan. 2020}
%\resumeDesc{Became the prize winner of the regional stage, in 3 months without
%knowledge of programming languages and algorithms}

\resumeSubHeadingListEnd

\section{Programming Skills}
\resumeSubHeadingListStart
\item{
\textbf{Languages}{: Go, Python, TypeScript }
}\vspace{-7pt}
\item{
\textbf{Technologies}{: K8S, SQL, Git, Docker, Bash, PostgreSQL, MongoDB, Redis, Kafka }
}
\vspace{-7pt}
\item{
\textbf{Knowledge}{: Algorithms, Data Structures, Operating Systems, Databases, Concurrency, Distributed Systems }
}
\resumeSubHeadingListEnd

\end{document}
